### 2025-09-18 README.Rmd

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![](https://r-pkg.org/badges/version/clarify)](https://cran.rstudio.com/package=clarify)
[![](https://cranlogs.r-pkg.org/badges/clarify)](https://cran.rstudio.com/package=clarify)
<!-- badges: end -->
